Flabby and injective objects in toposes

### 2018-06-14 paper-flabby-objects.tex
Pushforward of flabby objects

\begin{prop}Let~$f : \E \to \F$ be an open geometric morphism between
elementary toposes. Let~$X \in \E$ be a flabby object. Then~$f_*(X)$ is flabby
as well.\end{prop}

\begin{proof}Without loss of generality, it suffices to verify
condition~$({\star})$ for the terminal stage~$A = 1$. Let~$k : K \to 1$ be a
monomorphism in~$\F$ and let~$x : K \to f_*(X)$ be an arbitrary morphism.
Then~$f^*(k) : f^*(K) \to 1$ is a monomorphism in~$\E$ and~$x^t : f^*(K) \to X$
is a morphism in~$\E$. Since~$X$ is flabby, there is an epimorphism~$B \to 1$
in~$\E$ and a morphism~$y : B \to X$ such that the morphism~$f^*(K) \times B \to X
\times B \to B$ factors over~$y$. XXX
\end{proof}

>>>>

\begin{prop}\label{prop:pushforward-of-flabby-objects}
Let~$f : \F \to \E$ be a geometric morphism. If~$f_*$ preserves epimorphisms,
then~$f_*$ preserves flabby objects.\end{prop}

\begin{proof}Let~$X \in \F$ be a flabby object. Without loss of generality, it
suffices to verify condition~$({\star})$ for the terminal stage~$A = 1 \in \E$.
Let~$k : K \to 1$ be a monomorphism in~$\E$ and let~$x : K \to f_*(X)$ be an arbitrary morphism.
Then~$f^*(k) : f^*(K) \to 1$ is a monomorphism in~$\F$ and~$x^t : f^*(K) \to X$
is a morphism in~$\F$. Since~$X$ is flabby, there is an epimorphism~$B \to 1$
in~$\F$ and a morphism~$y : B \to X$ such that the morphism~$f^*(K) \times B
\to X$ factors over~$y$. Hence~$x$ factors over~$f_*(y) : f_*(B) \to f_*(X)$.
By assumption, the morphism~$f_*(B) \to f_*(1)$ is an epimorphism.
\end{proof}

The assumption on~$f_*$ of Proposition~\ref{prop:pushforward-of-flabby-objects}
is for instance satisfied if~$f$ is a local geometric morphism or if~$f$ is
induced by an open continuous injection between topological spaces. % XXX
